---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bugRzilla

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-CMD-check](https://github.com/llrs/bugRzilla/workflows/R-CMD-check/badge.svg)](https://github.com/llrs/bugRzilla/actions)
[![Codecov test coverage](https://codecov.io/gh/llrs/bugRzilla/branch/master/graph/badge.svg)](https://codecov.io/gh/llrs/bugRzilla?branch=master)
<!-- badges: end -->

The goal of bugRzilla is to provide a package to download and analyze the [R bug tracker](https://bugs.r-project.org/bugzilla/).

## Installation

You can install the released version of bugRzilla from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("bugRzilla")
```

## Example

This is a basic example which shows you the first "bug" on the issue tracker:

```{r example}
library(bugRzilla)
## basic example code
g1 <- get_issue(1)
g1[, 1:5]
```

## Other packages

Just after having figured out how to authenticate via the API I realized that someone might have done this before. After a brief search I found [bugtractr](https://github.com/mvkorpel/bugtractr/): It allows to access the same data (only non authenticated requests), last commit 3 years ago, no test coverage, but author is responsive. 
