---
title: "R bugs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R bugs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bugRzilla)
```

# Introduction

Some time ago the R core team [requested](https://developer.r-project.org/Blog/public/2019/10/09/r-can-use-your-help-reviewing-bug-reports/index.html) help with bugs in bugzilla. Some time later on a [thank you post](https://developer.r-project.org/Blog/public/2019/12/16/thanks-for-reviewing-bug-reports/index.html) they reported bugs closed over time. Which pointed out that we, users, package developer might not be helping enough. This packages tries to lower the barrier to improve R by finding bugs, testing and checking they are reproducible.

To do so this package is to support ease the interaction with bugzilla for a user who wants to:

-   see what happened/what's happening.

-   submit/validate/comment on existing issues.

To do so it uses the Bugzilla API[^1] and sometimes the accessible xml files.

[^1]: The full documentation of the API is [here](https://bugzilla.readthedocs.io/en/latest/api/index.html "API documentation").

# The package

## Authentication

Some queries do not require authenticatication but some do. To set up an authentication you'll need an user (You have to [ask one](mailito:bug-report-request@r-project.org)), and then create an API key.

``` {.r}
create_api_key()
```

This will ask you to save your API key to `.Renviron`. To check that the api key is working (after resetting the R session) you have:

``` {.r}
check_key()
```

## Getting data

If you don't want much information but want's to know about an issue you have `get_issue()` :

```{r get_issue}
issue1 <- get_issue(1)
issue1[, 1:5]
```
