---
title: "R bugs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R bugs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bugRzilla)
```

# Introduction

Some time ago the R core team [requested](https://developer.r-project.org/Blog/public/2019/10/09/r-can-use-your-help-reviewing-bug-reports/index.html) help with bugs in bugzilla.
Some time later on a [thank you post](https://developer.r-project.org/Blog/public/2019/12/16/thanks-for-reviewing-bug-reports/index.html) they reported bugs closed over time.
This packages tries to lower the barrier to improve R by helping filling and navigating bugs. 

This package is to support ease the interaction with bugzilla for a user who wants to submit/validate/comment on existing issues using the Bugzilla API[^1].

[^1]: The full documentation of the API is [here](https://bugzilla.readthedocs.io/en/latest/api/index.html "API documentation").

# Checking Bugzilla

We can check if there has been an update recently with:

```{r last_audit}
check_last_audit()
```

## Getting data

### Issues

To get information about which issues exists you can call `get_bug()` :

```{r bugs}
bugs <- get_bug(1:5)
head(bugs)
plot(bugs$id, bugs$creation_time, 
     main = "Bug ID vs creation time", xlab = "ID", 
     ylab = "Creation Time")
```

We can see that the first issue is created in 2010 while the next issues are from before 2000.
This is because the first issues is a test and next issues were ported from jitterbug.

We can also see that there are some blank spaces between bugs ids.
Perhaps some reports where deleted or simply they didn't got filled.

There's information about who created, about what, version, resolution, priority...

### Comments

We can now collect information about comments on issues:

```{r get-commenti}
get_comment(issue = 1)
```

Or if we know the id of the comment, of just that comment:

```{r get-commentc}
get_comment(comment = 1)
```

### Attachments

If you look carefully you'll see that the third comment on the first issue has an attachment id.
We can also explore what it is:

```{r get-attachment}
get_attachment(issue = 1)
# Similar to get_comment we can also do
# get_attachment(attachment = 1)
```

### History

If you want to know what changed you can with `get_history()` :

```{r get-history}
get_history(issue = 1)
```

## Authenticated operations

If you want to post or comment you'll need to be authenticated.
To set up an authentication you'll need a user (You have to ask for an account to bug-report-request\@r-project.org), and then create an API key.

``` {.r}
create_bugzilla_key()
```

This will ask you to save your API key to a configuration file.
To check that the api key is working you have:

``` {.r}
check_authentication()
```

Probably you'll want to validate a bug so you'll post a comment with

```{.r}
post_comment()
```

If you have found a bug you can create it with.

```{.r}
post_bug()
```

Note that this will guide you asking some questions before opening a bug report. 
